Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-06 paper/paper_new.tex
Updates from Overleaf

\begin{table*}[t]
    \centering
    \caption{Metadata properties}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale| & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|contrast| & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis| & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value| & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length| & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side| & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
    \centering
    \caption{Metadata properties (* indicates higher order properties)}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale|* & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|contrast|* & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis|* & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value|* & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length|* & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side|* & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table*}
